Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Change "my" to "our" to reflect that this is now a two author paper.
Point out a potential problem with the many-zeroes simplification, to justify the grouping approach.

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
%TODO: XXX why this could be a problem XXX.
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

@@

While the results could not definitely show the best grouping, it was clear that the appropriate grouping differed for the rows and columns.
That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
This should not be surprising, for it is known that different traits govern species competitive effects than their responses \parencite{goldberg1991competitive}.
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
My results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?

>>>>

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{wootton2016many}, and setting these to zero may lose important information.
Another approach assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

@@

While the results could not definitely show the best grouping, it was clear that the appropriate grouping differed for the rows and columns.
That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
This should not be surprising, for it is known that different traits govern species competitive effects than their responses \parencite{goldberg1991competitive}.
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
Our results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?
